lab_notebook

### 2018-11-17 lab_notebook.Rmd
playing with fishbase

@@

#chile_itq_turf <- filter(only_turf_itq, Country == "Chile")
unique(chile_itq_turf$SciName)
# 67

@@

>>>>

1 & 2
```{r}

@@

#chile_itq_turf <- filter(true_turf_itq, Country == "Chile")
#unique(chile_itq_turf$SciName)
# 67

@@

3
ISCAAP
```{r}

iscaap_cat_1 <- upside_2018_updated %>%
  select("SciName", "SpeciesCat")

iscaap_cat <- unique(iscaap_cat_1 [ , 1:2])

true_turf_itq_iscaap_1 <- merge(true_turf_itq, iscaap_cat, by = "SciName", all = T)

true_turf_itq_iscaap <- true_turf_itq_iscaap_1 %>%
  filter( itq != "NA" & ivq != "NA" & iq != "NA" & turf != "NA")

true_turf_itq_iscaap[is.na(true_turf_itq_iscaap)] <- "NA"

missing_speccat <- true_turf_itq_iscaap %>%
  filter(SpeciesCat == "NA")

determine_spec_cat <- as.vector(missing_speccat$SciName)
determine_spec_cat

FishBase

library("rfishbase")

species <- as.vector(true_turf_itq_iscaap$SciName)
species

table_species <- species(species)

#fishtest <- species_list(Genus = "Labroides")
#fishtest
#species(fishtest)
#even running the practice online tutorial get this error :Error in curl::curl_fetch_memory(url, handle = handle) : Timeout was reached: Connection timed out after 10004 milliseconds

#fishbase_test <- validate_names(species, fields = c("Species", ""))
